\chapter{The Religion of Mob-Worship or The War and Way out}

\begin{center}
    Frankreich's traurig Geschick, die Grossen\marginpar{\scriptsize here again modern spelling would differ: \emph{Gro\ss e} instead of \emph{Grosse}. Again I would leave it. To indicate the ``wrong'' spelling is in the original, you could, add \emph{[sic]}} m\"ogen's bedenken,\\
    Aber bedenken f\"urwahr sollen es Kleine noch mehr;\\
    Grossen gingen zu Grunde; doch wer besch\"utze die Menge \\
    Gegen die Menge? Da war Menge der Menge Tyrann. 
\end{center}
\hfill Goethe\cite{num27}.

Professor Lowes Dickinson of Cambridge University in an eloquent passage of his article on ``The War and the Way out," says: ``The future (the future of civilisation in Europe, he means) cannot be moulded to any purpose until the plain men and women, workers with their hands and workers with their brains in England and in Germany and in all countries get together and say to the people who have led them into this catastrophe and will lead them into such again and again, ``No more! No more! And never again! you rulers, soldiers and diplomats, you who through the long agony of history have conducted the destinies of mankind and conducted them to hell, we do now repudiate you.
Our labour and our blood have been at your disposal.
They shall be so no more.
You shall not make the peace as you have made the war.
The Europe that shall come out of this war shall be \emph{our} Europe.
And it shall be one in which another European war shall be never possible."

That is the dream of the socialists now in Europe.
But such a dream, I am afraid, can never be realised.
When the plain men and women in the countries of Europe get rid of the rulers, soldiers and diplomats and take into their own hands the question of peace and war with another country, I am perfectly sure, before that very question is decided, there will be quarrels, broken heads and wars between the plain men and women themselves in every country.
Take the case of the Irish question in Great Britain.
The plain men and women in Ireland in trying to take into their own hands the question even of how to govern themselves were actually flying at each others' throats and if this greater war had not come, would at this moment, be cutting each other's throats.

Now in order to find a way out of this war, we must first of all, find out the origin, the cause of this war; find out who was really responsible for this war.
Professor Dickinson would have us believe that it was the rulers, soldiers and diplomats who have led the plain men and women into this catastrophe, --- into this hell of a war.
But I think, I can prove, that it was not the rulers, soldiers and diplomats who have led the plain men and women into this war, but it was the plain men and women who have driven and pushed the poor helpless rulers, soldiers and diplomats of Europe into this hell of a war.\footnote{, in the original book}

Let us first take the case of the actual rulers, --- the Emperors, Kings and Presidents of Republic now in Europe.
Now it is an undisputed fact that with the exception perhaps of the Emperor of Germany, the actual rulers of the countries now at war have had no say whatever in the making of this war.
In fact the actual rulers of Europe today, Emperors, Kings and Presidents, bound in hand and foot\footnote{fool in the original book} and gagged by the mouth as they all are by Constitutions and Magna Chartas of Liberty, --- these actual rulers have no say whatever in the government or conduct of public affairs in their countries.
Poor King George of Great Britain, when he tried to say something to prevent a civil war over the Irish question, was peremptorily told by the plain men and women in Great Britain to hold his tongue and he had actually to apologise through his Prime Minister to the plain men and women for trying to do his duty as a King to prevent a civil war! 
In fact, the actual rulers of Europe today have become mere expensive ornamental figures as the figures on a seal with which Government official documents are stamped.
Thus being mere ornamental figures without any say or will of their own as far as the government of their countries is concerned, how can it be said, that the actual rulers of Europe are responsible for this war?

Let us next examine the soldiers whom Professor Dickinson and everybody now denounces for being responsible for this war.
Ruskin in addressing the cadets at Woolwich, say: ``The fatal error of modern\footnote{modem in the original book} institutions is to take away the best blood and strength of the nation, all the soul substance of it, that is brave, and careless of reward and scornful of pain and faithful in trust; and to cast that into steel and make a mere sword of it, \emph{taking away its voice and will}; but to keep the worst part of the nation, whatever is cowardly, avaricious, sensual, and faithless, and to give to this the authority, to this the chief privilege where there is the least capacity of thought.''
``The fulfilment of your vow for the defence of England,'' Ruskin went on to say addressing the soldiers of Great Britain, ``will by no means consist in carrying out such a system. You are no true soldiers if you only mean to \emph{stand at a shop door to protect shop boys who are cheating inside}.''
Now\footnote{Now is missing in the original book} Englishmen, and true English soldiers too, who denounce Militarism and Prussian Militarism, I think, should read and ponder over these words of Ruskin.
But what I want to say here is that it is evident from what Ruskin says here, that if the actual rulers in Europe have practically no say, the soldiers of Europe today have absolutely no say whatever in the government and conduct of affairs in their countries.
What Tennyson says of the British soldiers at Balaclava, is true of the poor soldiers now in this war, ``Theirs was not to reason why, theirs was but to do and die." 
In fact if the actual rulers in Europe today have become mere expensive ornamental figures, the soldiers in Europe now have become mere dangerous mechanical automatons.
Being more mechanical automatons without any voice or will of their own as far as the government of their countries is concerned, how then can it be said that the soldiers in Europe are responsible for this war?

Last of all, let us examine the case against the diplomats now in Europe.
Now, according to the theories of Government, the Magna\footnote{Magua in the original book} Chartas of Liberty and Constitutions of Europe, the diplomats --- the actual Statesmen and Ministers in charge of the government and conduct of public affairs in a country now are there merely to carry out the will of the people: in other words, merely to do whatever the plain men and women in the country tell them to do.
Thus we see that the diplomats, --- the Statesmen and Ministers in the Government of the countries in Europe today, have also become mere machines, talking machines; in fact mere puppets as in a Marionnettes show; puffed-up puppets without any will of their own, worked, pulled and moved up and down by the plain men and women.
Being mere hollow puffed-up puppets, with only a voice, but without any will of their own, how then can it be said that the diplomats, --- the Statesmen and Ministers now in\footnote{m in the original book} European countries are responsible for this war?

Indeed the most curious thing, it seems to me, in the government of all the European countries today is that every one who is actually in charge of the conduct of affairs in the Government, --- ruler, soldier as well as diplomat or Statesman and Minister, is not allowed to have any will of his own; not allowed to have any power to do what he thinks best for the security and good of the nation, but every plain man and woman, --- John Smith, editor of the ``Patriotic Times,'' Bobus of Houndsditch, once in Carlyle's time, sausage maker and jam manufacturer, but now owner of a big Dreadnought ship building yard, and Moses Lump, money lender, --- are given full power to have all their will and all the say in the government of the country; in fact, the power to tell the actual ruler, soldier and diplomat what they are to do for the good and security of the nation.
Thus you will find, if you go deep enough into the matter, that it is these three persons, --- John Smith, Bobus of Houndsditch and Moses Lump, who are responsible for this war.
For it was these three persons, John Smith, Bobus and Moses Lump, I want to point out here, who created that monstrous modern\footnote{modem in the original book} Machine, --- the modern Militarism in Europe, and it was this monstrous Machine which has brought on this war.

But now it will be asked why have the actual rulers, soldiers and diplomats of Europe so cowardly abdicated in favour of these three persons, John Smith, Bobus and Moses Lump?
I answer, because the plain men and women, --- even the good honest plain men and women, such men as Professor Dickinson, --- instead of giving their loyalty and support to the actual rulers, soldiers and diplomats of their country, have taken the side of John Smith, Bobus and Moses Lump against their own rulers, soldiers and diplomats.
The two reasons again why the plain men and women in Europe support and take\footnote{lake in the original book} the side of John Smith, Bobus and Moses Lump, are: first, because John Smith, Bobus and Moses Lump tell the plain men and women that they John Smith, Bobus and Moses Lump belong to the party of plain men and women; and, secondly, because the plain men and women in Europe from their childhood have been taught that the \emph{Nature of Man is evil}; that every man, whenever he is invested with power, will abuse his power; and further that every man as soon as he gets strong enough to be able to do it, will be sure to want to rob and murder his neighbour.
In fact, I want to say here the reason why John Smith, Bobus and Moses Lump have been able to get the plain men and women in Europe to help them to force the actual rulers, soldiers and diplomats of Europe to create the monstrous modern machine, which has brought on this terrible war, is because the plain men and women in every country, when in a crowd, are always selfish and cowardly.

Thus, if you go into the root of the matter, you will see that it is not the rulers, soldiers and diplomats, not even John Smith, Bobus and Moses Lump, but it is really the good honest plain men and women, such men as Professor Dickinson\footnote{Dickison in the original book} himself, who are responsible for this war.
But Professor Dickinson will repudiate and say: We plain men and women did not want this war.
But then, who wanted this war?
I answer, Nobody wanted this war.
Well then, what brought on this war?
I answer, It was panic which brought on this war; the panic of the mob, --- the panic which seized and took possession of the crowd of plain men and women in all European countries when last August that monstrous modern\footnote{modem in the original book} machine in Russia which the plain men and women had helped to create, began to move.
In short, it was panic, I say, --- the panic of the mob, panic of the crowd of the plain men and women communicating itself to and seizing and paralysing the brains of the rulers, soldiers and diplomats of the countries now at war and making them helpless which has brought on this terrible war.
Thus we see, it was not, as Professor Dickinson says, the rulers, soldiers and diplomats, who have conducted and led the plain men and women of Europe into this catastrophe, but it was the plain men and women, --- the selfishness, the cowardice and at the last moment, the funk, the panic of the plain men and women who have driven and pushed the poor helpless rulers, soldiers and diplomats of Europe into this catastrophe, --- into this hell of a war.
Indeed the tragic hopelessness of the situation now in Europe I want to say here, lies in the abject, pitiful, pitiable helplessness of the actual rulers, soldiers and diplomats of the countries now at war at the present moment.

It is evident therefore from what I have shown in the above, that if there is to be peace in Europe now and in the future, the first thing to be done is not, as Professor Dickinson says, to bring or call in, but to remove and keep out the plain men and women who, when in a crowd, are so selfish and cowardly; who are so liable to panic whenever the question of peace and war arises.
In other words, if there is to be peace in Europe, the first thing to be done, it seems to me, is to protect the rulers,\footnote{' in the original book} soldiers and diplomats from the plain men and women; to protect them from the mob, --- the panic of the crowd of plain men and women which makes them helpless.
In fact, not to speak of the future, if the present actual situation now in Europe is to be saved, the only way to do it, it seems to me, is first to rescue the rulers, soldiers and diplomats of the countries now at war, from their present helplessness.
The tragic hopelessness of the situation now in Europe, I wish to point here, is that everybody wants peace, but nobody has the courage or power to make peace.
I say therefore, the first thing to be done is to rescue the rulers, soldiers and diplomats from their present helplessness; to find some means to give them \emph{power}, --- power to find a way to make peace.
That, I think, can be done only in one way and that is for the people of Europe, --- for the people of the countries now at war, to tear up their present Constitutions and Magna Chartas of Liberty, and make a new Magna, Charta --- a \emph{Magna Charta of Loyalty-such} as we Chinese have in our Religion of good citizenship here in China.

By this new Magna Charta of Loyalty, the people of the countries now at war must swear: first not to discuss, meddle or interfere in any way with the politics of the present war; secondly, absolutely to accept, submit to and abide by whatever terms of peace their actual rulers may decide upon among themselves.
This new Magna Charta of Loyalty, will at once give the actual rulers of the countries now at war power and, with power, courage to make peace; in fact, power and courage at once to order and command peace.
I am perfectly sure that as soon as this power is given them, the actual rulers of the countries now at war, will at once order and command peace.
I say, I am perfectly sure of this, because the rulers of the countries now at war, unless they are absolute incurable lunatics or demons, which everybody must admit that they are not, --- no, not even, I will venture to say here, the most slandered man now in Europe, the Emperor of Germany, --- they, the rulers of the countries now at war, must see that for them together to continue to spend nine million pounds sterling of the blood and sweat-earned money  of their people everyday in\footnote{m in the original book} order to slaughter the lives of thousands of innocent men and to destroy the homes and happiness of thousands of innocent women, is really nothing but \emph{infernal madness}.
The reason why the rulers, soldiers and diplomats of the countries now at war cannot see this, is because they feel themselves helpless; helpless before the panic of the mob, --- the panic of the crowd of plain men and women; in fact, as I said because the panic of the crowd, --- the panic of the mob has seized and paralysed their brains.
I say therefore the first thing to be done, if the present actual situation now in Europe is to be saved, is to rescue the rulers, soldiers and diplomats of the countries now at war from the panic of the mob, --- the panic of the crowd of plain men and women by giving them power.

The tragic hopelessness of the situation now in Europe, I want to say here further, lies not only in the helplessness of the rulers, soldiers and diplomats, but also in the helplessness of everybody in the countries now at war.
Everybody is helpless and cannot see that this war, wanted by nobody and brought on only by the panic of the mob, is an infernal madness, because, as I said, the panic of the mob has seized and paralysed the brains of everybody.
One can see this even in Professor Dickinson, who writes to inveigh against the war, ---\footnote{-- in the original book} to denounce the rulers, soldiers and diplomats for bringing on this war.
Professor Dickinson too, without being conscious of it, has the panic of the mob in his brain.
He begins his article by stating that this article of his is not a ``stop\footnote{slop in the original book} the war" paper.
He goes on to say: ``Being in the war, I think, as all Englishmen think, we must go on fighting until we can emerge from it with our territory and security intact and with the future peace of Europe assured as far as human wisdom can assure it."
The integrity and security of the British Empire and the future peace of Europe to be obtained only by going on indefinitely spending nine million pounds sterling of good money and slaughtering thousands of innocent men everyday!
The monstrous absurdity of such a proposition, I believe, has only to be stated, to be seen by any one who has not the panic of the mob in his brain.
The peace of Europe!
Why, I think if this rate of spending and slaughtering goes on for any length of time, there will certainly be peace, but no Europe left on the map of the world.
Indeed if there is anything which will show how really and utterly unfit the plain men and women are to decide on the question of peace and war, this attitude of mind of a man even like Professor Dickinson conclusively shows it.

But the point I want to insist upon here, is that everybody even in the countries now at war wants peace, but nobody has the \emph{power} to make peace, to stop the war.
Now the fact that nobody has the power to make peace, to stop the war, makes everybody believe that there is no possible way of making peace; makes everybody despair of the possibility of making peace.
\emph{This despair of the possibility of making peace} it is which prevents everybody in the countries now at war from seeing that this war wanted by nobody and brought on only by the panic of the mob, is really nothing but an infernal madness.
The first thing to be done, therefore, in order to make everybody see that this war is nothing but an infernal madness is to show everybody that there \emph{is a possibility of making peace}.
In order to make everybody see that there is a possibility of making peace, the very first and simple thing to do is at once to stop the war; to invest some one with full power to stop the war; to invest the rulers of the countries now at war with \emph{absolute power} by making, as I said, a Magna Charta of Loyalty, --- absolute power to order and command the war to be stopped at once.
As soon as everybody sees that the war \emph{can} be stopped, everybody in the countries now at\footnote{al in the original book} war, everybody except perhaps a few absolute incurable lunatics, will be able to see that this war wanted by nobody and brought on only by the panic of the mob, --- is really nothing but an infernal madness; that this war, if continued, will be ruinous even to the countries which will emerge victorious from it.
As soon as the rulers of the countries now at war have the power to stop the war and everybody in the countries now at war sees and realises that this war is an infernal madness, it will then and \emph{only then} be not only possible, but easy for a man like President Wilson of the United States to make a successful appeal, as the Ex-President Rosevelt\footnote{Roosevelt in the original book} did during the Russo-Japanese war, to the rulers of the countries now at war to order and command the war to be stopped at once and then to find a way to make a permanent peace.
I\footnote{1 in the original book} say it will be easy then for a man like President Wilson to make a \emph{successful} appeal for peace because, I believe, in order to make peace, the only important thing the rulers of the countries now at war will have to do is, to build a special lunatic asylum and arrest and clap into it the few absolute incurable lunatics, --- men like Professor Dickinson who have the panic of the mob in the brain, --- the panic for the integrity and security of the British Empire and the future peace of Europe!

Thus, I say, the one and only way out of this war, is for the people of the countries now at war, to tear up their present Magna Chartas of Liberty and Constitutions, and make a new Magna Charta, a Magna Charta not of Liberty, but a Magna Charta of Loyalty, such as we Chinese have in our Religion of good citizenship here in China.

To prove the efficacy of what I now propose, let me here call the attention of the people of Europe and America to the fact that it was the \emph{absolute loyalty} of the people of Japan and Russia to their rulers which made it possible for the Ex-President Rosevelt\footnote{Roosevelt in the original book} to make a \emph{successful} appeal to the late Emperor of Japan and the present Emperor of Russia to stop the Russo-Japanese war and to command and order the peace to be made at Portsmouth.
This absolute loyalty of the people in the case of Japan is secured by the Magna Charta of Loyalty in our Chinese Religion of good citizenship which the Japanese learnt from us.
But in Russia where there is no Religion of good citizenship with its Magna Charta of Loyalty\footnote{loyalty in the original book}, the absolute loyalty of the Russian people has to be secured by the power of the \emph{Knout}.

Now see what happened, after the Treaty of Portsmouth, in a country with a Religion of good citizenship and its Magna Charta of Loyalty, like Japan, and a country without such a Religion and such a Charta like Russia.
In Japan, after the Treaty of Portsmouth, the plain men and women in Tokyo, whose Religion of good citizenship had been spoilt by the New Learning of Europe, raised a clamour and tried to create a panic, --- but the Magna Charta of Loyalty in the hearts of the true unspoilt Japanese people with the help of a few policemen in one day put down the clamour and panic of the plain men and women and there has been not only internal peace in Japan but peace in the Far East ever since\cite{num28}. 
But in Russia after the Treaty of Portsmouth, the plain men and women everywhere in the country, also raised a clamour and tried to create a panic, and, because there is no Religion of good citizenship in Russia, the \emph{Knout}, --- which secured the absolute loyalty of the Russian people, \emph{broke} and thus ever since the plain men and women in Russia have had full liberty to make riots and Constitutions, to raise clamour and create panic, --- panic for the integrity and security of the Russian Empire and the Slavonic race and for the future peace of Europe!
The result of all this was that when a petty difference of opinion arose between the Austrian Emperor and the Emperor of Russia over the degree of punishment to be meted out for the people responsible for the murder of the Austrian Arch-Duke, the plain men and women, the mob in Russia were able to raise such a clamour and create such a panic for the integrity and security of the Russian Empire, $\&$c. that the Emperor of Russia and his immediate advisers were driven to mobilise the whole Russian army, in other words, to move that monstrous modern\footnote{modem in the original book} machine created by John Smith, Bobus and Moses Lump. 
When that monstrous modern machine, --- the modern\footnote{modem in the original book} Militarism in Russia, began to move, there was immediately a general panic among the plain men and women in all Europe and it was this general panic among the plain men and women in Europe seizing and paralysing the brains of the rulers and diplomats of the countries now at war and making them helpless, which, as I have already shown, brought on this terrible war.

Thus the real origin of this war, if you go deep into the very root of the matter, was the Treaty of Portsmouth.
I say the Treaty of Portsmouth was origin of this war, because after that Treaty, the \emph{Knout}, --- the power of the Knout, --- in Russia \emph{broke} and there was nothing to protect the Emperor of Russia from the plain men and women, --- from the panic of the crowd of plain men and women, --- in fact, from the panic of the mob in Russia, --- the panic of the mob for the integrity and security of the Russian Empire and the Slavonic race!
The German poet Heine with wonderful insight considering that he was the most liberal of all Liberals, in fact the Champion of the Liberalism of his time, says: "The Absolutism in Russia is really a Dictatorship rather than anything else with which to bring into life and make possible the carrying out of the liberal ideas of our modern\footnote{modem in the original book} times (der Absolutismus in Russland ist vielmehr eine Dictatur um\footnote{urm in the original book} die liberalen Ideen unserer neuesten Zeit in's Leben treten zu lassen)".
In fact, I say again, after the Treaty of Portsmouth the Dictatorship, --- the \emph{Knout}, the power of the Knout in Russia \emph{broke} and there was nothing to protect the ruler, soldier and diplomat of Russia from the mob, --- that, I say, was the real origin of this war.
In other words, the real origin and cause of this war was the \emph{fear of the mob in Russia}.

In Europe in the past the responsible rulers of all the European countries were able to maintain civil order in their own countries and to keep international peace in Europe, because they feared and worshipped God.
But now, I want to say, the rulers, soldiers and diplomats in all European countries of today instead of fearing and worshipping God, fear and worship the mob, --- fear and worship the crowd of plain men and women in their country.
The Russian Emperor, Alexander I, who made the Holy Alliance in Europe after the Napoleonic wars, was able not only to maintain civil order in Russia, but to keep international peace in Europe, because he feared God.
But the present Emperor in Russia is not able to maintain civil order in his own country and to keep international peace in Europe, because, instead of fearing God, he fears the mob.
In Great Britain rulers like Cromwell, were able to maintain civil order in their own country and to keep international peace in Europe, because they worshipped God.
But the actual rulers of Great Britain today, responsible Statesmen like Lord Grey, Messrs Asquith\footnote{Messrs. Asquith in the original book}, Churchill and Loyd George, are not able to maintain civil order in their own country and keep international peace in Europe, because, instead of worshipping God, they worship the mob, --- worship not only the mob in their own country, but also the mob in other countries.
The late Prime Minister of Great Britain Mr. Campbell Bannerman, when the Russian Duma was dissolved, shouted at the top of his voice, ``\emph{Le Duma est mort. Vive le Duma!}"

I have said that the real origin and cause of this war was the fear of\footnote{of is missing in the original book} the mob in Russia.
Now I want to say here that, real \emph{first} origin and cause of this war was not the fear of the mob in Russia.
The first origin and cause, --- the \emph{fons et origo} not only of this war, but of all the anarchy, horror and misery in the world today, --- is the worship of the mob, the worship of the mob now in all European countries and in America, --- especially in Great Britain.
It was the worship of the mob in Great Britain which caused and brought on the Russo-Japanese war\cite{num29}.
After the Russo-Japanese war came the Treaty of Portsmouth and the Treaty of Portsmouth, with the help of the shout of the British Prime Minister, broke the \emph{Knout}, --- the power of the Knout, broke what Heine calls the Dictatorship and created the fear of the mob in Russia which, as I said, has brought on this terrible war.
It is, I may incidentally say here, this worship of the mob in Great Britain, this worship of the mob among Englishmen and foreigners in China; in fact this Religion of the worship of the mob imported from Great Britain and America into China, --- which has brought on the Revolution and the present nightmare of a Republic in China now threatening to destroy  the most valuable asset of civilisation of the world today, the real Chinaman. 
I say therefore that this worship of the mob in Great Britain --- this Religion of the worship of the mob in Europe and America today, unless it is at once put down, will destroy not only the civilisation of Europe, but all civilisation in the world.  

Now, I say, the only thing, it seems to me, which can and will put down this worship of the mob, this Religion of the worship of the mob which now threatens to destroy all civilisation in the world today --- is this Religion of Loyalty, --- the Sacrament, the Magna Charta of Loyalty such as we Chinese have in our Religion of good citizenship here in China.
This Magna Charta of Loyalty will protect the responsible rulers, soldiers and diplomats of all countries from the mob, and enable them not only to maintain civil order in their own countries but also to keep peace in the world.
What is more, this Magna Charta of Loyalty, --- this Religion of good citizenship with its Magna Charta of Loyalty, by enabling all good men and true to help their legitimate rulers to awe and keep down the mob --- will enable the rulers of all countries to keep peace and maintain order in their own countries and in the world without the Knout, without policeman, without soldier; in one word without militarism.

Now before I conclude, I want to say a word about militarism, about German militarism.
I have said that first origin and cause of this war was the worship of the mob in Great Britain.
Now I want to say here that if the first origin and cause of this war was the worship of the mob in Great Britain, the \emph{direct} and immediate cause of this war was the \emph{worship\footnote{-worship in the original book} of might} in Germany.
The Emperor of Russia is reported to have said before he signed the order for the mobilisation of the Russian army, ``We have stood this for seven years. Now it must finish."
These passionate words of the Emperor of Russia show how much he and the Russian nation must have suffered from the worship of might of the German nation.
Indeed the worship of the mob in Great Britain, as I said, broke the \emph{Knout} in the hands of the Emperor of Russia which made him helpless against the mob who wanted war and the worship of might of the German nation made him lose his temper which drove him to go in with the mob for war.
Thus we see the real cause of this war was the worship of the mob in Great Britain and the worship of might in Germany.
The Bible in our Chinese Religion of good citizenship says ``\emph{Do not go against what is right, to get the praise of the people. Do not trample upon the wishes of the people to follow your own desires.}''\cite{num30} 
Now to go against what is right to get the praise of the people, is what I have called the worship of the mob, and to trample upon the wishes of the people to follow your own desires, is what I have called the worship of might.
But with this Magna Charta of Loyalty, the responsible ministers and Statesmen in a country will feel themselves responsible not to the mob, not to the crowd of plain men and women, but \emph{to their King and their Conscience} and this will protect them from the temptation to go against what is right to get the praise of the people, --- in fact protect them from mob worship.
The Magna Charta of Loyalty again will make the rulers of a country feel the awful responsibility which the great power given them by Magna Charta of Loyalty imposes upon them and this will protect them from the temptation to trample upon the wishes of the people to follow their own desires, --- in fact protect them from the worship of might.
Thus we see this Magna Charta of Loyalty, --- this Religion of good citizenship with its Magna Charta of Loyalty, will help to put down the worship of the mob and the worship of might, which, as I have shown, are the cause of this war.

The French Joubert who had lived through the French Revolution in answer to the modern\footnote{modem in the original book} cry for liberty said: ``Let your cry be for free souls rather than for free men.
Moral liberty is the one vitally important liberty, the liberty which is indispensable; the other liberty is good and salutary only so far as it favours this.
\emph{Subordination is in itself a better thing than independence. The one implies order and arrangement; the other implies only self sufficiency with isolation.}
The one means harmony, the other, a single tone; the one, is the whole, the other is but the part."

This then, I say, is the one and only way for the people of Europe, for the people of the countries now at war, not only to get out of this war, but\footnote{hut in the original book} to save the civilisation of Europe, --- to save the civilisation of the world, and that is for them now to tear up their present Magna Chartas of liberty and Constitutions, and make a new Magna Charta, --- a Magna Charta not of liberty, but a Magna Charta of Loyalty; in fact to adopt the Religion of good citizenship with its Magna Charta of Loyalty such as we Chinese have here in China.

AB INTEGRO SAECLORUM NASCITUR ORDO! \marginpar{\scriptsize 世界的秩序将重新诞生}
       
     
   


    
