
\begin{thebibliography}{30}
    \bibitem[1]{num1} Mencius says, ``What I hate in your clever men is that they always distort things. 所恶于智者为其凿也 Bk~IV. Part II.~26,''
    \bibitem[2]{num2} The best book written in any European Language on the spirit of the Chinese civilisation is a book called ``La Cit\'e Chinoise" by G.-Eug.~Simon who was once French Consul in China. It was from this book that Prof. Lowes Dickinson of Cambridge, as he himself told me, drew his inspiration in writing his famous ``Letters from John Chinaman."
    \bibitem[3]{num3} The famous telegram of the German Emperor to President Kruger was an instinctive outburst of indignation of the true Gernamic soul with its moral fibre against Joseph Chamberlain and his Cockney class in England, who manipulated the Boer War.
    \bibitem[4]{num4} Confucius said to a disciple ``when outside nations are dissatisfied with you, you should cultivate civil or Civic virtues (远人不服则修文德)" The British aristocracy, however, like the Manchu aristocracy in China, are now helpless against the mob and mob worshippers in England. But it is, I must say, a great credit to the British aristocracy that not one of them as far as I know, has joined the mob in England in their shout, bowl and yell in this war.
    \bibitem[5]{num5} To show what a mob the Chinese returned students have become, I may mention here that some of these students in Peking last year actually wrote letters to the ``Peking Gazette,'' a newspaper conducted by a clever Chinese ``Babu'' by the name of Eugene Chen, openly threatening to organise and carry out a public assault upon me for criticising the new Chinese woman in my essay on ``the Chinese woman.'' This clever Chinese ``Babu'' Eugene Chen the instigator of the contemplated piece of rowdyism now is a respected member of the Committee of the Anglo-Chinese Friendship Bureau under the patronage of the British Minister and the I.~G. of the Chinese Customs!
    \bibitem[6]{num6} Emerson with great insight, says, "What sent Napoleon to St.~Helena, was not loss of battles, but the parvenu, the vulgar ambition in him --- the vulgar ambition to marry a real Princess, to found a dynasty.
    \bibitem[7]{num7} Confucius says, ``Possession of power without leniency and generosity is a thing which I never can bear to see. (居上不宽吾何以观之) Shakespeare says: \\``Oh, it is glorious\\ To have a giant's strength: but it is tyrannous \\ To use it like a giant.'' See note p.15.
    \bibitem[8]{num8} That is to say, all who depend and put their faith solely upon material brute force o Emerson says, who believe in the vulgar musket worship.
    \bibitem[9]{num9} The German Minister Baron Kettler during the fanatic Boxer outbreak was accidentally killed by a madman from the fanatic soldiery. As madman, the German diplomats insisted upon branding the whole Chinese national on the forehead with an indelible mark of humiliation, by Having this Kettler memorial erected in the principal street of the Chinese Capital. The late Court Cassini, Russian Minister in Peking just before the Boxer outbreak, said in an interview with an American journalist, ``The Chinese are a \emph{polite people}, but the impoliteness of British and German Ministers, especially of the German Minister in Peking is something outrageous."
    \bibitem[10]{num10} Confucius says, ``The moral man, the gentleman by living a life of simple truth and earnestness bring peace to the world (君子笃恭而天下平)" 
    \bibitem[11]{num11} \begin{center}
    Aren't just doing the right thing? \hfill the mob we must befool them;\\
    See now, how shiftless! and look now how wild! for such is the mob.\\
    Shiftless and wild all sons of Adam are when you befool them;\\
    Be but honest and true, and thus make human, them all. \hfill --- Goethe\\
\end{center} 
    \bibitem[12]{num12} The first sentence of the first book that is put into the hands of every child in China when he goes to school
    \bibitem[13]{num13} 唯有民众懂得什么是真正的生活，唯有民众过着真正的人的生活.
    \bibitem[14]{num14} Mencius Bk.~III, Part II IX, $_{\text{II}}$.
    \bibitem[15]{num15} 中庸 --- The universal order XII 4.
    \bibitem[16]{num16} 论语 --- Discourses and Sayings Chap.~II 4.
    \bibitem[17]{num17} 论语 --- Doscourses and Sayings Chap.~XX 3.
    \bibitem[18]{num18} 中庸 --- The Universal order XII $_{\text{I}}$.
    \bibitem[19]{num19} 中庸 --- The Universal order I.~$_\text{I}$.
    \bibitem[20]{num20} 道可道非常道， 名可名非常名
    \bibitem[21]{num21} 论语 --- Discourses and Sayings Chap.~XV 28.
    \bibitem[22]{num22} Mencius, speaking of the two purest and most Christlike characters in Chinese history, said: ``When men heard of the spirit and temper of Po-yi and Shu-ch'i, the dissolute ruffian become unselfish and the cowardly man had courage.''
    \bibitem[23]{num23} 中庸 The Universal Order XIII
    \bibitem[24]{num24} ``Der Philister negiert nicht nur andere Zustande als der seining ist, er will auch dass alle ubrigen Menschen auf seine Weise existieren sollen,'' --- GOETHE
    \bibitem[25]{num25} Compare\footnote{Compared in the original book} another saying of Confucius 巧言令色 \emph{Ch'iao yen ling se}, plausible speech and fine \emph{manners} (Discourses and Sayings Ch.~I.~3.)
    \bibitem[26]{num26} Higher Education: Known among foreigners as the ``Great Learning''
    \bibitem[27]{num27} \begin{center}
    Dreadful is France's misfortune, the Classes should truly bethink them, \\
    But still more of a truth, the Masses should lay it to heart.\\
    Classes were smashed up; well then, but who will protect now the Masses\\
    'Gainst the Masses? Against the Masses the Masses did rage. \\
\end{center}
    \bibitem[28]{num28} Peace in the Far East, I say, until lately the mob-worshipping Statesmen of Great Britain got their apt pupils the now also mob-worshipping Statesmen of Japan, men like count Okuma, who is the greatest mob-worshipper now in Japan, --- to make war against a handful of German clerks in Tsingtau!
    \bibitem[29]{num29} The panic of the mob in Great Britain, --- especially the selfish panic of the British mob in Shanghai and in China whose mouthpiece then was the ``great" Dr.~Morrison, the ``Times" correspondent in Peking, with their shout for the ``open door" in Manchuria alarmed and incited the Japanese into the Russo-Japanese war.
    \bibitem[30]{num30} 罔违道以干百姓之誉, 罔拂百姓以从己之欲 \\ Shu-king or Canon of History in the Confucian Bible: part II ch. 1.6
\end{thebibliography}
