\chapter{Introduction}
\begin{center}
    \emph{The Religion of Good-citizenship}
\end{center}
\begin{center}\footnotesize
   Sage, thun \marginpar{\scriptsize thun [sic: tun]} wir nicht recht? Wir m\"ussen den P\"obel betr\"ugen,\\
   Sieh\footnote{Sich in the original book} nur, wie ungeschickt, sich nur wie wild er sich zeigt!\\
   Ungeschick und wild sind alle rohen Betrogenen;\\
   Seid nur redlich und fuhrt ihn zum Menschlichen an.\\
    \hfill Goethe\cite{num11}.
\end{center}

The great war at the present moment is absorbing all the attention of the world exclusive of everything else.
But then I think this war itself must make serious thinking people turn their attention to the great problem of civilisation.
All civilisation begins by the conquest of Nature, \ie\, by subduing and controlling the terrific physical forces in Nature so that they can do no harm to men.
The modern civilisation of Europe today has succeeded in the conquest of Nature with a success, it must be admitted, hitherto not attained by any other civilisation.
But there is in this world a force more terrible even than the terrific physical forces in Nature and that is the passions in the heart of man.
The harm which the physical forces of Nature can do to mankind, is nothing compared with the harm which human passions can do.
Until therefore this terrible force, --- the human passions --- is properly regulated and controlled, there can be, it is evident, not only no civilisation, but even no life possible for human beings.

In the first early and rude stage of society, mankind had to use physical force to subdue and subjugate human passions.
Thus hordes of savages had to be subjugated by sheer physical force.
But as civilisation advances, mankind discovers a force more potent and more effective for subduing and controlling human passions than physical force and this force is called \emph{moral force}\footnote{``moral force'' in the original book}.
The moral force which in the past has been effective in subduing and controlling the human passions in the population of Europe, is Christianity.
But now this war with the armament preceding it, seems to show that Christianity has become ineffective as a moral force.
Without an effective moral force to control and restrain human passions, the people of Europe have had again to employ physical force to keep civil order. As Carlyle truly says, ``Europe is Anarchy plus a constable."
The use of physical force to maintain civil order leads to militarism.
In fact militarism is necessary in Europe today\footnote{10-day in the original book} because of the want of an effective moral force.
But militarism leads to war and war means destruction and waste.
Thus the people of Europe are on the horns of a dilemma\footnote{{\huge$\cdot$} in the original book}.
If they do away with militarism, anarchy will destroy their civilisation, but\footnote{hut in the original book} if they keep up militarism, their civilisation will collapse through the waste and destruction of war.
But Englishmen say that they are determined to put down Prussian militarism and Lord Kitchner \marginpar{\scriptsize Kitchner [sic: Kitchener] \\ Horatio Herbert Kichener: (1850-1916) a senior British Army officer and colonial administrator.} believes that he will be able to stamp out Prussian militarism with three million drilled and armed Englishmen.
But then it seems to me when Prussian militarism is thus stamped out, there will then arise another militarism, --- the British militarism which again will have to be stamped out.
Thus there seems to be no way of escape out of this vicious circle.

But is there really no way of escape?
Yes, I believe there is.
The American Emerson \marginpar{\scriptsize Ralph Waldo Emerson: (1803-1882) an American essayist, lecturer, poet.} long ago said, ``I can easily see the bankruptcy of the vulgar musket worship, --- though great men be musket-worshippers; and 'tis\footnote{it in the original book} certain, as God liveth, the gun that does need another gun,\footnote{. in the original book} the law of love and justice alone can effect a clean revolution."
Now if the people of Europe really want to put down militarism, there is only one way of doing it and that is, to use what Emerson calls the gun that does not need another gun, the law of love and justice, --- in fact, moral force, With an effective moral force, militarism will become unnecessary and disappear of itself.
But now, that Christianity has become ineffective as a moral force the problem is where are the people of Europe to find this new effective moral force which will make militarism unnecessary?

I believe the people of Europe will find this new moral force in China, --- in the Chinese civilisation.
The moral force in the Chinese civilisation which can make militarism unnecessary is the Religion of good citizenship.
But\footnote{Hut in the original book} people will say to me, ``There have also been wars in China."
It is true there have been wars in China; but, since the time of Confucius 2,500 years ago, we Chinese have had no militarism such as that we see in Europe today.
In China war is an accident, whereas in Europe war has become a necessity.
We Chinese are liable to have wars, but we do not live in constant expectation of war.
In fact the one thing intolerable in the state of Europe, it seems to me, is not so much war as the fact that every body is constantly afraid that his neighbour as soon as he gets strong enough to be able to do it, will come to rob and murder him and he has therefore to arm himself or pay for an armed policeman to protect him.
Thus what weighs upon the people of Europe is not so much the accident of war\footnote{War in the original book}, but the constant necessity to arm themselves, the absolute necessity to use physical force to protect themselves.

Now in China because we Chinese have the Religion of good citizenship a man does not feel the need of using physical force to protect himself; he has seldom the need even to call in and use the physical force of the policeman, of the State to protect him.
A man in China is protected by the sense of justice of his neighbour; he is protected by the readiness of his fellow men to obey the sense of moral obligation.
In fact, a man in China does not feel the need of using physical force to protect himself because he is sure that right and justice is recognised by every body as a force higher than physical force and moral obligation is recognised by every body as something which must be obeyed.
Now if you can get\footnote{gent in the original book} all mankind to agree to recognise right and justice, as a force higher than physical force, and moral obligation as something which must be obeyed, then the use of physical force will become unnecessary; then there will be no militarism in the world.
But of course there will be in every country a few people, criminals, and in the world, a few savages who will not or are not able to recognise right and justice as a force higher than physical force and moral obligation as something which must be obeyed.
Thus against criminals and savages a certain amount of physical or police force and militarism will always be necessary in every country and in the world.

But people will say to me how are you to make mankind recognise right and justice as a force higher than physical force.
I answer the first thing you will have to do is to convince mankind of the efficacy of right and justice, convince them that right and justice is a power; in fact, convince them of the \emph{power of goodness}.
But then again how are you to do this?
Well, --- in order to do this, the Religion of good citizenship in China teaches every child as soon as he is able to understand the meaning of words, that \emph{the Nature of man is good}\cite{num12}.

Now the fundamental unsoundness of the civilisation of Europe today\footnote{to-day in the original book}, it seems to me, lies in its wrong conception of human nature; its conception that human nature is evil and because of this wrong conception, the whole structure of society in Europe has always rested upon force.
The two things which the people of Europe have depended upon to maintain civil order are Religion and Law.
In other words, the population of Europe have been kept in order by the fear of God and the fear of the Law.
Fear implies the use of force.
Therefore in order to keep up the fear of God, the people of Europe had\footnote{Had in the original book} at first to maintain a large number of expensive idle persons called \emph{priests}.
That, to speak of nothing else, meant so much expense, that it at last became an unbearable burden upon the people.
In fact in the thirty years war of the Reformation, \marginpar{\scriptsize Reformation was a schism in Western Christianity initiated by Martin Luther and continued by Huldrych Zwingli, John Calvin and other Protestant Reformers in 16th-century Europe.} the people of Europe tried to get rid of the priest.
After having got rid of the priests who kept the population in order by the fear of God, the people of Europe tried to maintain civil order by the fear of the Law.
But to keep up the fear of the Law, the people of Europe have had to maintain\footnote{main lain in the original book} another class of still more expensive idle persons called \emph{policemen and soldiers}.
Now the people of Europe are\footnote{arc in the original book} beginning to find out that the maintenance of policemen and soldiers to keep civil order, is still more ruinously expensive than even the maintenance of priests.
In fact, as in the thirty years war of the Reformation, the people of Europe wanted to get rid of the priest, so in this present war, what the people of Europe really want, is to get rid of the soldier.
But the alternatives before the people of Europe if they want to get rid of the policeman and soldier, is either to call back the priest to keep up the fear of God or to find something else which, like the fear of God and the fear of the Law, will help them to maintain civil order.
That, to put the question broadly, I think, everybody will admit, is the great problem of civilisation before the people of Europe after this war.

Now after the experience which they have had with the priests, I do not think the people of Europe will want to call back the priests.
Bismarck \marginpar{\scriptsize Otto Eduard Leopold (1815-1898), known as Otto von Bismarck, was a conservative Prussian statesman who dominated German and European affairs from the 1860s until 1890.} has said, ``We will never go back to Canossa."
Besides, even if the priests are now called back, they would be useless, for the fear of God is gone from the people of Europe.
The only other alternative before the people of Europe therefore, if they want to get rid of the policeman and soldier, is to find something else, which, like the fear of God and the fear of the Law, can help them to maintain civil order.
Now this something, I believe, as I have said, the people of Europe will find in the Chinese civilisation.
This something is what I have called the Religion of good citizenship.
This Religion of good citizenship in China is a religion which can keep the population of a country in order without priest and without policeman or soldier.
In fact with this Religion of good citizenship, the population of China, a population as large, if not larger than the whole population of the Continent of Europe, are actually and practically kept in peace and order without priest and without policeman or soldier.
In China, as every one who has been in this country knows, the priest and the policeman or soldier, play a very subordinate, a very insignificant part in helping to maintain public order.
Only the most ignorant class in China require the priest and only the worst, the criminal class in China, require the policeman or soldier to keep them in order.
Thus I say if the people of Europe really want to get rid of Religion and Militarism, of the priest and soldier which have caused them so much trouble and bloodshed, they will have to come to China to get this, what I have called the Religion of good citizenship.

In short what I want to call the attention of the people of Europe and America to, just at this moment when civilisation seems to be threatened with bankruptcy, is that there is an invaluable and hitherto unsuspected asset of civilisation here in China.
The asset of civilisation is not the trade, the railway, the mineral wealth, gold, silver, iron or coal in this country.
The asset of civilisation of the world today, I want to say here, is the Chinaman, --- \emph{the unspoilt real Chinaman} with his Religion of good citizenship. The real Chinaman, I say, is an invaluable asset of civilisation, because \emph{he is a person who costs the world little or nothing to keep him in order}.
Indeed I would like here to warn the people of Europe and America not to destroy this invaluable asset of civilisation, not to change and spoil the real Chinaman as they are now trying to do with their New Learning.
If the people of Europe and America succeed in destroying the real Chinaman, the Chinese type of humanity; succeed in transforming the real Chinaman into a European or American, i.e., to say, a person who will require a priest or soldier to keep him in order, then surely they will increase the burden either of Religion or of Militarism of the world, --- this last item at this moment already becoming a danger and menace to civilisation and humanity.
But on the other hand, suppose one could by some means or other change the European or American type of humanity, transform the European or American into a real Chinaman who will then not require a priest or soldier to keep him in order, --- just think what a burden will be taken off from the world.

But now to sum up in a few plain words the great problem of civilisation in Europe arising out of this war.
The people of Europe, I say, at first tried to maintain civil order by the help of the priest.
But after a while, the priest cost too much expense and trouble.
The people of Europe then, after the thirty years war, sent away the priest and called in the policeman and soldier to maintain civil order.
But now they find the policeman and soldier are causing more expense and trouble even than the priests.
Now what are the people of Europe to do?
Send away the soldier and call back the priest?
No, I do not believe the people of Europe will want to call back the priest.
Besides the priest now would be useless.
But then what are the people of Europe to do?
I see Professor Lowes Dickinson \marginpar{\scriptsize Goldsworthy Lowes Dickinson (1862 – 1932), known as Goldie, was a British political scientist and philosopher.} of Cambridge in an article in the Atlantic Monthly, entitled ``The War and the Way out," say: ``Call in the \emph{mob}.''
I am afraid the mob when once called in to take the place of the priest and soldier, will give more trouble than even the priest and the soldier.
The priests and soldiers in Europe have caused wars, but the mob will bring revolution and anarchy and then the state of Europe will be worse than before.
Now my advice to the people of Europe is: Do not call back the priest, and for goodness sake don't call in the mob, ---\footnote{-- in the original book} but call in the Chinaman; \emph{call in the real Chinaman with his Religion of good citizenship and his experience of 2,500 years how to live in peace without priest and without soldier.}

In fact I really believe that the people of Europe will find the solution of the great problem of civilisation after this war, --- here in China. 
There is, I say here again, an invaluable, but hitherto unsuspected asset of civilisation here in China, and the asset of civilisation is the real Chinaman. 
The real Chinaman is an asset of civilisation because he has the secret of a new civilisation which the people of Europe will want after this great war, and the secret of that new civilisation is what I have called the Religion of good citizenship. 
The first principle of this Religion of good citizenship is to believe that the \emph{Nature of Man is good}; to believe in the power of goodness; to believe in the power and efficacy of what the American Emerson calls the law of love and justice. 
But what is the law of love? The Religion of good citizenship teaches that the law of love means to \emph{love your father and mother}. 
And what is the law of justice? 
The Religion of good citizenship teaches that the law of justice means to be true, to be faithful, to be loyal; that the woman in every country must be selflessly, absolutely loyal to her husband, that the man in every country must be selflessly, \emph{absolutely loyal to his sovereign}, to his King or Emperor. 
In fact the highest duty in this Religion of good citizenship I want to say finally here is the \emph{Duty of Loyalty}, loyalty not only in deed, but loyalty in spirit or as Tennyson \marginpar{\scriptsize Alfred Tennyson: (1809-1892) Poet Laureate of Great Britain and Ireland, one of the most popular British poets.} puts it,
\begin{quote}\footnotesize
    To reverence the King as he were\\
    Their conscience and their conscience as their King,\\
    To break the heathen and uphold the Christ.\\
\end{quote}
