\chapter{Preface}
The object of this book is an attempt to interpret the spirit and show the value of the Chinese civilisation.
Now in order to estimate the value of a civilisation, it seems to me, the question we must finally ask is not what great cities, what magnificent houses, what fine roads it has built and is able to build; what beautiful and comfortable furniture, what clever and useful implements, tools and instruments it has made and is able to make; no, not even what institutions, what arts and sciences it has invented: the question we must ask, in order to estimate the value of a civilisation, --- is, \emph{what type of humanity}, what kind of men and women it has been able to produce.
In fact, the man and woman, --- the type of human beings --- which a civilisation produces, it\footnote{U in the original book} is this which shows the essence, the personality\footnote{personality9 in the original book}, so to speak, the soul of that civilisation.
Now if the men and women of a civilisation show the essence, the personality and soul of that civilisation, the language which a man and woman speak, shows the essence, the personality, the soul of the man and woman.
The French say of literary composition, ``\emph{Le style, c'est l'\footnote{L in the original book}homme.}"
I have therefore taken these three things, the Real Chinaman, the Chinese woman and the Chinese language, --- as the subjects of the first three essays in this volume to illustrate the spirit and show the value of the Chinese civilisation.

I have added to these, two essays in which I have tried to show how and why men, foreigners who are looked upon as authorities on the subject, do not really understand the real Chinaman and the Chinese language.
The Rev.~Arthur Smith, who wrote the Chinese Characteristics, I have tried to show, does not understand the real Chinaman, because, being an American, --- he is not deep enough to understand the real Chinaman.
Dr.~Giles again, who is considered a great sinologue\footnote{Sinologue in the original book}, I have tried to show does not really understand the Chinese language, because, being an Englishman, he is not broad enough, --- he has not the philosophic insight and the broadness which that insight gives, I have wanted to include in this volume an\footnote{and in the original book} essay I wrote on J. B. Bland and Backhouse's book on the famous late Empress Dowager, but unfortunately I have not been able to find a copy of that essay which was published in the ``National Review" in Shanghai some four years ago.
In that essay, I have tried to show that, such men as J. B. Bland and Backhouse do not and cannot understand the real Chinese woman, --- the highest type of woman produced by the Chinese civilisation viz the late Empress Dowager, because such men as J. B. Bland and Backhouse are not simple, --- have not the simplicity of mind, being too clever and having, like all modern men, a distorted intellect\cite{num1}. 
In fact, in order to understand the real Chinaman and the Chinese civilisation, a man must be deep, broad and simple, for the three characteristics of the Chinese character and the Chinese civilisation are: depth, broadness and simplicity.

The American people, I may be permitted to say here, find it difficult to understand the real Chinaman and the Chinese civilisation, because the American people, as a rule, are broad, simple, but not deep.
The English cannot understand the real Chinaman and Chinese civilisation because the English, as a rule, are deep, simple, but not broad.
The Germans again cannot understand the real Chinaman and the Chinese civilisation because the Germans, especially the educated Germans, as a rule, are deep, broad, but not simple.
The French, --- well the French are the people, it seems to me, who can understand and has understood the real Chinaman and the Chinese civilisation best\cite{num2}. 
The French, it is true, have not the depth of nature of the Germans nor the broadness of mind of the Americans nor the simplicity of mind of the English, --- but the French, the French people have to a preeminent \marginpar{\scriptsize preeminent [sic: pre-eminent]} degree a quality of mind such as all the people I have mentioned above as a rule, have not, --- a quality of mind which, above all things, is necessary in order to understand the real Chinaman and the Chinese civilisation; a quality of mind viz: \emph{delicacy}, For, in addition to the three characteristics of the real Chinaman and Chinese civilisation which I have already mentioned, I must here add one more, and that the chief characteristic, namely delicacy; delicacy to a preeminent \marginpar{\scriptsize preeminent [sic: pre-eminent]} degree such as you will find nowhere else except perhaps among the ancient Greeks and their civilisation.

It will be seen from what I have said above that the American people if they will study the Chinese civilisation, will get depth; the English, broadness; and the Germans, simplicity; and all of them, Americans, English and Germans by the study of the Chinese civilisation, of Chinese books and literature,  will get a quality of mind which, I take the liberty of saying here that it seems to me, they all of them, as a rule, have not to a preeminent degree,\marginpar{\scriptsize preeminent [sic: pre-eminent]} namely, \emph{delicacy}.
The French people finally, by the study of the Chinese civilisation, will get all, --- depth, broadness, simplicity and a still finer delicacy than the delicacy which they now have.
Thus the study of the Chinese civilisation, of Chinese books and literature will, I believe, be of benefit to all the people of Europe and America.
I have therefore added to this volume an essay on Chinese scholarship, ---\footnote{-- in the original book} the sketch of a programme how to study Chinese, which I made for myself when I made up my mind and began, after my return from Europe, to study the civilisation of my own country, exactly now thirty years ago; this sketch of a programme how to study Chinese which I hope will be of help to those who want to study Chinese and the Chinese civilisation.

Last of all, I have included as an appendix an essay on practical politics, --- an essay on ``The War and the Way out."
Knowing full well the danger of entering into the arena of practical politics, I nevertheless do it, because in order to prove the value of the Chinese civilisation, I want to show how the study of the Chinese civilisation can help to solve the problem facing the world today, --- the problem of saving the civilisation of Europe from bankruptcy.\footnote{, in the original book} 
In fact I want to show that the study of Chinese, of Chinese books and Chinese literature is not only a hobby for sinologues\footnote{Sinologues in the original book}.

In this essay, I have tried to show the moral causes which have brought on this war; for until the true moral causes of this war are understood and remedied, there can be no hope of finding a way out of it.
The moral causes of this war, I have tried in my essay to show, are the \emph{worship\footnote{- worship in the original book} of the mob} in Great Britain and the \emph{worship of might} in Germany.
I have, in\footnote{m in the original book} my essay, laid emphasis more upon the worship of the mob in\footnote{m in the original book} Great Britain, than the worship of might in Germany, because looking impartially upon the question, it seems to me that it is the worship of\footnote{ol in the original book} the mob in Great Britain, which is responsible for the worship of might in Germany; in fact, the worship of the mob in all European countries and especially in Great Britain, it was this which has created the enormous German Militarism which everybody now hates and denounces.

Now let me first of all say here that it is the \emph{moral fibre} in the German nation, their intense love of righteousness and, as a\footnote{a is missing in the original book} consequence, their equally intense hatred of unrighteousness, hatred of all untidiness and disorder (Unzucht und Unordnung)\footnote{(Unzuchut und Unordnung) is missing in the original book}, which makes the German people believe in and worship might.
All men who intensely love righteousness, who intensely hate unrighteousness are inclined to believe in and worship might.
The Scotch Carlyle, for instance, believed in and worshipped might.
Why?
Because Carlyle with the German moral fibre in him intensely hated unrighteousness.
Now the reason why I say that it is the worship of the mob in Great Britain which is responsible for the worship of might in Germany, is because, the \emph{moral fibre} --- the intense hatred of unrighteousness, of untidiness and disorder in the German nation makes them hate the mob, the worship of the mob and the mob worshippers in Great Britain.\footnote{{\huge$\cdot$} in the original book} 
After the German nation saw how the mob and the mob-worshipping politicians of Great Britain made the Boer war\footnote{War in the original book} in Africa, their \emph{instinctive} intense hatred\cite{num3} for the mob, the mob-worship and the mob-worshippers in Great Britain made the German nation willing to make heavy sacrifices, made the \emph{whole German nation ready to starve themselves to create a Navy} with the hope to put down the mob, the mob-worship and the mob-worshippers in Great Britain.
In fact, the German nation, I may say, found themselves surrounded on all sides by the mob, mob-worship and mob-worshippers encouraged by Great Britain in all Europe and this made the German nation believe more and more in might, made the German nation worship might as the only salvation for mankind.
This worship of\footnote{ol in the original book} might in Germany created by the hatred for the Religion of mob worship in Great Britain, thus created the enormous monstrous German Militarism which everybody now hates and denounces.

Thus, I say again, it is the worship of the mob, the Religion of the worship of the mob in all European countries, especially in Great Britain, which is responsible for the worship of might in Germany; which has created the abnormous enormity and monstrosity of German Militarism in Europe today.
If therefore the people in Great Britain and the people in all European countries and America want to put down German Militarism --- they must try first to put down the mob, the mob-worshippers and the Religion of mob-worship in their own countries\cite{num4}. 
To the people of Europe and America, and in Japan and China too, today who speak of and want liberty, I will venture here to say that the only way, it seems to me, to get liberty, true liberty is to behave themselves; to learn to behave themselves properly.
Look at China before this Revolution.
There was more liberty among the Chinese people, --- no priest, no policeman, no Municipal tax, no income tax to bother them --- more liberty among the Chinese than among any other people in the world; and why?
Because the Chinese people before this Revolution behaved themselves; knew how to behave themselves; knew how to behave themselves as \emph{good citizens}.
But now after this Revolution ---\footnote{-- in the original book} there is less liberty in China, and why?
Because the modern\footnote{modem in the original book} queueless, up-to-date Chinamen, the returned students have learnt from the people of Europe and America, --- learnt from the European mob in Shanghai how to \emph{misbehave themselves}; to behave themselves not as good citizens, but as a \emph{mob} --- a mob encouraged, coddled and worshipped by the British diplomats and the British Inspector General of Customs in Peking\cite{num5}. 
In fact, what I want to say here is, that if the people in Europe, the people in Great Britain want to put down German Militarism, Prussian Militarism, they must keep the mob in their own countries in order; they must make the mob in their own countries behave themselves properly; in fact they must put down the Religion of mob-worship, and the mob-worshippers in their own countries.

But now while I say that the British people with their mob worship and encouragement of mob-worship are responsible for the worship of might in Germany, for German Militarism, I must at the same time say here that, looking again impartially upon the question, it seems to me that the \emph{direct} responsibility for this war rests more heavily upon the German people, upon the German nation, than upon anybody else.

In order to understand this, let me first of all here give the history of German Militarism in Europe.
After the Reformation and the Thirty Years War, the Germanic nations, the people of the Germanic race with their \emph{moral fibre},\footnote{ã€in the original book} with their intense love of righteousness and their intense hatred of unrighteousness, hatred of all untidiness and disorder, the German people, with Militarism as a sword in their hand, became the rightful guardian of civilisation in Europe.
In other words, the responsibility for putting order and tidiness (Zucht und Ordnung) in Europe; in fact, the \emph{moral hegemony} so to speak of Europe came into the hands of the German people.
After the Reformation, Frederick the Great, like Cromwell in England, had to take up and use the sword of German Militarism to put order and tidiness in Europe and he succeeded in putting order and tidiness at any rate in the Northern part of Europe.
Now see what happened after Frederick the Great's death.
His successor did not know how to use the sword of German Militarism in order to guard and protect the civilisation of Europe; in fact, he was unfit to hold the moral hegemony of Europe. 
The result was, the whole of Europe, even the courts in Germany became a bottomless pit of abominations covered up only with the veneer of civilisation; so much so that at last the suffering population, the plain men and women in France rose up with pikes to protest against the abominations.
The plain men and women in France who rose up to protest against the abominations very soon became a \emph{mob}, and this mob finally found a great and able leader, Napoleon Buonaparte\cite{num6}, who led them to rob, murder, kill and ravage all Europe until the nations in Europe rallying round the small nucleus of \emph{sound} German Militarism left in Europe, put an end to the career of the great leader of the mob at Waterloo.
After this the moral hegemony of Europe should have returned to the people of the Germanic race, to the Prussians, the back bone of the German nations.
But the jealousy of the other races which formed the Austrian Empire prevented this.
The result was that without the German nation with its moral fibre and the sword of German Militarism to keep down the mob, the mob in 1848 again rose up furiously\footnote{Curiously in the original book} to break the civilisation of Europe.
Then again the German nation --- the backbone of the Germanic nations, the Prussians with their moral fibre and the sword of German Militarism, saved Europe, --- saved Kingship, (Bismarck called it the dynasty), saved civilisation in Europe from the mob.

But now the Austrians, --- the other races forming the Austrian Empire again became jealous and would not allow the German nation, --- the backbone of the Germanic nations, Prussia to take over the moral hegemony of Europe until 1866 when the Prussian King Wilhelm with Bismarck and Moltke had to put down the Austrian jealousy by force and took over the hegemony into their hands.
After this, Louis Napoleon, not like his great uncle a leader, but a swindler of the mob or, as Emerson calls him, a successful thief, tried with the mob of Paris behind him, to dispute and wrest the moral hegemony of Europe from the German nation.
The result was that the Emperor Wilhelm with the sharp sword of German militarism in his hand had to march to Sedan and put down the poor successful thief and swindler of the mob.
The plain men and women of Paris who put their trust in the mob and the swindler of the mob had their houses sacked and burnt \emph{not by the German Militarism}, not by the Germans and Prussians, but by the very mob in whom they put their trust.
After 1872, --- not only the moral, but the actual political hegemony of Europe passed finally into the hands of the German nation with the moral fibre of the Germanic race in their soul and the sword of German Militarism in their hand, to hold down the mob and keep the peace in Europe and thanks to the moral fibre in the German nation and the sword of German Militarism, Europe since 1872 has now enjoyed peace for 43 years.
Thus people who abuse and denounce German Militarism and Prussian Militarism should remember how much Europe owes to this very German, this Prussian Militarism which they now abuse and denounce.

I have in the above taken the trouble to give this rough short sketch of the German Militarism in Europe in order to make the German people see that I am not prejudiced against them in saying what I am going to say to show that the actual \emph{direct} responsibility for this war rests more heavily upon them, upon the German people and German nation than upon anybody else.
I say that the actual \emph{direct} responsibility for this war rests more heavily upon the German people and German nation than upon anybody else; and why? --- Because \emph{power means responsibility}\cite{num7}. 

I say that it is the intense love of righteousness, the intense hatred of unrighteousness, intense hatred of all untidiness and disorder (Unzucht und Unordnung) in the German people which makes them believe in and worship might.
Now I want to say here that this hatred of unrighteousness, hatred of untidiness and disorder, when it becomes over-intense, when it is carried to excess becomes also an \emph{unrighteousness}, becomes a frightful and terrible unrighteousness, something more sinful and wrong even than untidiness and disorder.
It was this over intense hatred of unrighteousness which came from their intense love of righteousness, the intense, narrow, hard, rigid hatred of unrighteousness carried to excess in the old Hebrew people --- the Hebrew people to whom the people of Europe owe their knowledge and love of righteousness, it was this which destroyed the Jewish nation.
It was from this over-intense narrow, hard, rigid hatred of unrighteousness that Jesus Christ came to save His people.
Christ, with what Matthew Arnold calls his unspeakable sweet reasonableness said to his own people: ``Learn of me, that I am \emph{mild} and lowly and ye\footnote{yet in the original book} shall have peace in your souls.''
But the Jews --- his own people would not listen to him; they, instead of listening to him, crucified him and the consequence was --- the Jewish nation perished.
To the Romans who were then the guardians of civilisation in Europe, Christ said, ``All they that take the sword shall perish with the sword!''\cite{num8} 
But the Romans would not listen, but instead, allowed\footnote{all owed in the original book} the Jews to crucify him.
The consequence was --- the Roman Empire and the old civilisation of Europe perished and passed away.
Goethe says: ``What a long way mankind must have travelled before they came to know how to deal gently even with sinners, to be merciful to law-breakers, \emph{and to be human even to the inhuman}.
Truly they were men of Divine nature who first taught this and who gave their lives for it in order to make the realisation of this possible and to hasten the practice of it.
``(Welchen Weg musste\footnote{mussle in the original book} nicht die Menschheit machen, bis sie dahin gelangte, auch gegen Schuldige\footnote{Seluldige in the original book} gelind, gegen Verbrecher schonend, gegen auch Unmenschliche menschlich zu sein. Gewiss waren as M\"anner\footnote{Manner in the original book} g\"ottlicher Natur, die dies zuerst lehrten\footnote{lehrlen in the original book}, die ihr Leben damit zubrachten, die Aus\"ubung\footnote{Ausiibung in the original book} m\"oglich zu machen und zu beschleunigen\footnote{beschleumgen in the original book}.)"

With those words of their great Goethe I will enture\marginpar{\scriptsize enture [sic]} here to appeal to the German people, to the German nation and say to them that, unless they find a way to put down their narrow, hard, rigid, excessive hatred of unrighteousness which makes them believe so absolutely in and worship might, unless they put away their absolute belief in and worship of might --- they, the German nation, like the Jewish nation, will perish and what is more, the modern\footnote{modem in the original book} civilisation of Europe for want of a strong guardian, will collapse and pass away just as the ancient civilisation of Europe passed away.
For it is this over-intense, narrow hard, rigid hatred of unrighteousness which makes the German people, the German nation believe in and worship might; and it is this absolute belief in and worship of might which makes the German nation, the German diplomats, German officials and the German people so inconsiderate and tactless in their behaviour towards other people.
When my German friends have asked me to show them a proof of the German worship of might, of German tactlessness, I have simply pointed the Kettler memorial in Peking to them.
The Kettler memorial in Peking is a standing monument of the German worship of might, of the tactlessness of the German diplomacy, the tactlessness of the German nation in their international dealings with other nations\cite{num9}.  
It was this worship of might of the German nation, this tactlessness of the German diplomacy of which the Kettler memorial is a standing monument, which made the Emperor of Russia say: ``We have stood this for seven years; now it must finish;" this tactlessness of the German diplomacy which made the really peace-loving Emperor of Russia and the best people in Europe, the soundest, most loveable, kindest and most generous-hearted people in Europe the Russians take the side of the mob and mob-worshippers in Great Britain and in France, which created the Triple-Entente; which made the Russians finally take the side even of the anarchic mob in Servia and thus brought on this war.
In one word it is this tactlessness of the German diplomacy, of the German people, of the German nation which is \emph{directly} responsible for this war.

I say therefore, if the German nation at this moment the true, rightful and legitimate guardian of the modern\footnote{modem in the original book} civilisation of Europe today\footnote{to-day in the original book}, is not to perish and the modern\footnote{modem in the original book} European civilisation is to be saved, --- the German nation, the German people must find a way to put down their over-intense, narrow, hard, rigid hatred of unrighteousness which makes them believe so absolutely in and worship might; in fact they must find a way to put down their absolute belief in and worship of might which makes them so inconsiderate and tactless.
But then, where are the German nation, the German people to find a way to put down their absolute belief in and worship of might?
The German nation,\footnote{>> in the original book} the German people, I say, will find this in these words of their great Goethe.
Goethe says: ``\emph{There are two peaceful powers in this world: Right and Tact}. (Es gibt zwei friedliche Gewalten auf der Welt: Das Recht und die Schicklichkeit.)'' 

Now this Right and Tact, \emph{das Recht und die Schicklichkeit}, is the essence of the Religion of good citizenship which Confucius gave to us Chinese here in China; this Tact, this \emph{Schicklichkeit}, especially, is the essence of the Chinese civilisation.
The Religion in the civilisation of the Hebrew people taught the people of Europe the knowledge of Right, but it did not teach Tact.
The civilisation of Greece taught the people of Europe the knowledge of Tact but it did not teach Right.
But the Religion in the civilisation of China teaches us Chinese both Right and Tact, --- das Recht und die Schicklichkeit.
The Hebrew Bible, the plan of civilisation according to which the people of Europe have built their present modern\footnote{modem in the original book} civilisation, teaches the people of Europe to love righteousness, to be righteous men, to do right.
But the Chinese Bible ---\footnote{-- in the original book} the Five Canons and Four Books in China, the plan of civilisation which Confucius saved for us the Chinese nation, teaches us Chinese also to love righteousness; to be righteous men; to do right, but it adds: ``Love righteousness, be righteous men, do right ---\footnote{-- in the original book} but \emph{with good taste}."
In short, Religion in Europe says: ``Be a good man."
But the Religion in China says: ``Be a good man \emph{with good taste}."
Christianity says: ``Love Mankind."
But Confucius says: ``Love Mankind \emph{with good taste}."
This Religion of righteousness with good taste, which I have called the Religion\footnote{religion in the original book} of good citizenship, is the new religion I believe, which the people of Europe, especially the people of the countries now at war, want at this moment not only to put an end to this war, but to save the civilisation of Europe, to save the civilisation of the world.
This new Religion, the people of Europe will find here in China, --- in the Chinese civilisation.
I have therefore in this little book made the attempt to interpret and show the value of this, --- the Chinese civilisation.
I do this with the hope that all educated serious thinking people, who read this book of mine will, by reading this book, better understand the moral causes of this war and understanding the moral causes of this war, will all help to put an end to this cruel, inhuman, useless and most monstrous war which the world has ever seen.

Now if we want to help to put an end to this war, we must, all of us, try to put down first the worship of the mob and then the worship of might in the world today, which, as I have said, are the cause of this war.
We can put down the worship of the mob, only when in our daily life, in everything we say and do, every one of us will think, not of interests, of expediency --- \emph{of what will pay}, but think of that word in Goethe's saying --- \emph{Right}.
Confucius says: ``The gentleman understands \emph{right}; the \emph{cad} understands \emph{interests}, --- \emph{what will pay}."
Further we can only put down the worship of the mob in the world when we have the courage, even if it does not pay to do so, to refuse to join and go in with the crowd --- with the \emph{mob}.
Voltaire says: ``C'est le malheur des gens honn\^etes qu'ils sont des laches.
It is the misfortune of so-called good people that they are cowards."
For it is\footnote{Ls in the original book} the selfishness and cowardice in all of us, I want to say here, selfishness which makes us think of interests, of expediency, of what will pay, instead of right, and cowardice which makes us afraid to stand up alone against the crowd, against the mob, --- it is this selfishness and cowardice in all of us which has given rise and created the mob and the worship of the mob in the world today\footnote{to-day   in the original book}.
People say German Militarism is the enemy and danger of the world today.
But I say it is the selfishness and cowardice in all of us which is the real enemy of the world today\footnote{to-day in the original book}: selfishness and cowardice in all of us, which, when combined, becomes Commercialism.
It is this spirit of Commercialism, in all countries of the world, especially in Great Britain and America, which is the real enemy of the world today. 
It is, I say, this spirit of Commercialism in\footnote{m in the original book} all of us and not Prussian Militarism which is the real, the greatest enemy of the world today.
For it is this Commercialism, a combination of selfishness and cowardice which has created the Religion of the worship of the mob and it is this Religion of the worship of the mob in Great Britain which has created the Religion of the worship of might in Germany, created the German Militarism which, as I said, finally brought on this war.
\emph{The fons et origo} of this war, I say, therefore is not militarism, but \emph{Commercialism}, which, as I said, is a combination of selfishness and cowardice in all of us.
Thus, if we want to help to put an end to this war, we must, all of us, first put down the spirit of Commercialism, the combination of selfishness and cowardice in us; in short, we must first of all, think of \emph{right} and not of interests and then have the courage to stand up against the crowd, against the mob.
In this way, I say, and \emph{only in this way} we can help to put down the worship of the mob, the Religion of the worship of the mob and in putting down this worship of the mob, this Religion of the worship of the mob, we can help to put an end to this war.

Now as soon as we have put down the worship of the mob, it will then be very easy to put down the worship of might, easy to put down German Militarism, put down Prussian Militarism.
The only thing we will have to do, in order to put down the worship of might, to put down German, Prussian or any Militarism in the world, is to think of the other word in that saying of Goethe --- \emph{Schicklichkeit, Tact, Good Taste} and, in thinking of that, to behave with tact and good taste, in short to behave properly; for might, Militarism, even Prussian Militarism can do nothing and will soon find itself useless and unnecessary against people who know how to behave themselves properly.
This then is the essence of the Religion of good citizenship; this is the secret of the Chinese civilisation.
This is also the secret of the new civilisation of Europe which the German Goethe gave to the people of Europe and the secret of this civilisation\footnote{libation in the original book} is: to put down force, not by force, but by \emph{right and tact}; in fact\footnote{(act in the original book} to put down force and everything that is evil in this world, not by force, but by ordering our conversation aright and behaving ourselves properly; and ordering our conversation aright and behaving properly means \emph{to do right and to behave with tact and good taste}\cite{num10}. 
This is the secret, the soul of the Chinese civilisation, the essence of the spirit of the Chinese people, which I have tried in this book to interpret and explain.

Finally I will here conclude with the words with which I concluded the book ``Papers from a\footnote{2 in the original book} Viceroy's Yamen" which I wrote after the Boxer trouble in China.
They are the words of the French poet B\'eranger and I think they are very appropriate at the present moment.
\begin{quote}\footnotesize
    J'ai vu la Paix descendre sur la terre,\\
    Semant de l'or des fleurs et des \'epis;\\
    L'air \'etait calme et du Dieu de la guerre\\
    Elle \'etouffait les foudres assoupis.\\
    Ah! disait-elle, egaux par la vaillance.\\
    Anglais, Fran\c{c}ais, Belge, Russe ou Germain,\\
    Peuples, formez une sainte alliance\\
    Et donnez vous la main!\\
\end{quote}

\vspace{2cm}
\hfill KU HUNG-MING
\vspace{3cm}
\emph{Peking, 20th, April, 1915.}

